Gap formation and stability in non-isothermal self-gravitating discs

### 2014-06-16 paper/results.tex
Added preliminary findings of longterm behaviour and short term as well as figures

>>>>

Long term simulation of vortices were done for $\tilde{\beta}=0.1,1.0$ and
 $\hat{\nu}=10^{-6},10^{-8},10^{-9}$ up to a total of 2000 orbits. Values
 of higher $\tilde{\beta}$ resulted generally in longer vortex lifetimes.
 The inviscid cases also were characterized by a sudden death of vortices
 while the higher viscosity case showed a gradual decrease in mode amplitudes
 attributed to the vortices.

Short term simulations of the linear phase of instability growth also distinguished
 the different effects of cooling rates. Simulations with higher
 $\tilde{\beta}$ were characterized by slower growth rates centered at the
 $m=2$ mode, lower density pertibations and vortex locations, and a more unitary aspect
 ratio for the vortices.

 \begin{figure}
   \includegraphics[scale=.42]{figures/stability_vis9betalow.ps}
   \caption{Mode intensity relative to $m=0$ for $\hat{\nu}=10^{-9}$ and $\tilde{\beta}=0.1$.}
 \label{stability_vis9lowb}
 \end{figure}

\begin{figure}
   \includegraphics[scale=.42]{figures/stability_vis9betamed.ps}
   \caption{Same as Fig. \ref{stability_vis9lowb} but $\hat{\nu}=10^{-9}$ and $\tilde{\beta}=1.0$. }
 \label{stability_vis9medb)}
 \end{figure}

\begin{figure}
   \includegraphics[scale=.42]{figures/stability_vis6betalow.ps}
   \caption{Same as Fig. \ref{stability_vis9lowb} but $\hat{\nu}=10^{-6}$ and $\tilde{\beta}=0.1$. }
 \label{stability_vis6lowb)}
 \end{figure}

\begin{figure}
   \includegraphics[scale=.42]{figures/stability_vis6betamed.ps}
   \caption{Same as Fig. \ref{stability_vis9lowb} but $\hat{\nu}=10^{-6}$ and $\tilde{\beta}=1.0$. }
 \label{stability_vis6medb)}
 \end{figure}
Same as \ref{stability_vis9lowb} but $\hat{\nu}=10^{-6}$ and $\tilde{\beta}=1.0$. 
\begin{figure}
   \includegraphics[scale=.60]{figures/analysis_sigma50lowb.ps}
   \caption{Density pertibation of disk at time=$50t_p$ with $\hat{\nu}=10^{-9}$ and $\tilde{\beta}=0.1$. }
 \label{shortterm_lowb)}
 \end{figure}

\begin{figure}
   \includegraphics[scale=.60]{figures/analysis_sigma50highb.ps}
   \caption{Density pertibation of disk at time=$50t_p$ with $\hat{\nu}=10^{-9}$ and $\tilde{\beta}=10.0$. }
 \label{shortterm_highb)}
 \end{figure}
